---
title: "Analysis"
author: "Václav Ocelík"
date: "`r Sys.Date()`"
output: html_document
---

<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
h1.title {
  font-size: 38px;
  text-align: center;
}
h4.author { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  text-align: center;
}
h4.date { /* Header 4 - and the author and data headers use this too  */
  font-size: 18px;
  text-align: center;
</style>

```{r setup, include=FALSE, message = F, echo = F}
knitr::opts_chunk$set(echo = T, message = F, error = F,
                      dpi = 300, fig.width = 6, fig.height = 4,
                      warning = F)
```

<body>

```{r}
library(tidyverse)
library(kableExtra)
theme_set(theme_classic())
```

Outliers
```{r}
df_outliers_control_group <- do.call(rbind, lapply(Sys.glob("../Control Group/Data/outliers/*.csv"), read_csv)) %>% 
  mutate(tournament = "control group")

df_outliers_complete_heterogeneity <- do.call(rbind, lapply(Sys.glob("../Complete Heterogeneity/Data/outliers/*.csv"), read_csv)) %>%
  mutate(tournament = "complete heterogeneity")

df_outliers_chaning_SDM <- do.call(rbind, lapply(Sys.glob("../Changing SDM/Data/outliers/*.csv"), read_csv)) %>%
  mutate(tournament = "changing SDM")
```

Combine outliers

```{r}
outliers <- df_outliers_complete_heterogeneity %>%
  rbind(df_outliers_control_group) %>%
  rbind(df_outliers_chaning_SDM)
```

Cooperation rates

```{r}
df_control_group <- do.call(cbind, lapply(Sys.glob("../Control Group/Data/*.csv"), read_csv)) %>%
  janitor::clean_names() %>%
  mutate(tournament = "control group",
         round = row_number()) %>%
  pivot_longer(seed_1024:seed_8, names_to = "Seed") 

df_complete_heterogeneity <- do.call(cbind, lapply(Sys.glob("../Complete Heterogeneity/Data/*.csv"), read_csv)) %>%
  janitor::clean_names() %>%
  mutate(tournament = "complete heterogeneity",
         round = row_number()) %>%
  pivot_longer(seed_1024:seed_8, names_to = "Seed")

df_changing_SDM <- do.call(cbind, lapply(Sys.glob("../Changing SDM/Data/*.csv"), read_csv)) %>%
  janitor::clean_names() %>%
  mutate(tournament = "changing SDM",
         round = row_number()) %>%
  pivot_longer(seed_1024:seed_8, names_to = "Seed")
```

Combine cooperation rates
```{r}
coop_rates <- df_control_group %>%
  rbind(df_complete_heterogeneity) %>%
  rbind(df_changing_SDM) %>%
  mutate(Seed = str_remove(Seed, "seed_"))
```

---

Geom lines and geom points are not useful.

```{r}
coop_rates %>%
  mutate(seed = as.factor(Seed)) %>%
  ggplot() +
  geom_point(aes(round, value, color = seed)) +
  facet_wrap(~tournament) +
  labs(title = "Average cooperation ratio per seed per tournament type.",
       x = "coop ratio",
       y = "round") +
  xlim(1000,9000)

coop_rates %>%
  mutate(seed = as.factor(Seed)) %>%
  ggplot() +
  geom_line(aes(round, value, color = seed)) +
  facet_wrap(~tournament) +
  labs(title = "Average cooperation ratio per seed per tournament type.",
       x = "coop ratio",
       y = "round") +
  xlim(1000,9000)
```

Smooth functions __are__ useful.

```{r}
coop_max <- coop_rates %>%
    group_by(tournament) %>%
    summarise(max_coop = max(value))

coop_rates %>%
  mutate(seed = as.factor(Seed)) %>%
  ggplot() +
  geom_smooth(aes(round, value, color = seed), se = F) +
  facet_wrap(~tournament) +
  labs(title = "Average cooperation ratio per seed per tournament type.",
       x = "coop ratio",
       y = "round") +
  xlim(1000,9000)
```

```{r}
coop_rates %>%
  mutate(seed = as.factor(Seed)) %>%
  ggplot() +
  geom_smooth(aes(round, value), color = "black") +
  facet_wrap(~tournament) +
  labs(title = "Average cooperation ratio per seed per tournament type.",
       x = "coop ratio",
       y = "round") +
  xlim(1000,9000)
```

```{r eval = F}
coop_rates %>%
  mutate(seed = as.factor(Seed)) %>%
  ggplot() +
  geom_point(aes(round, value), color = "black") +
  facet_wrap(~tournament) +
  labs(title = "Average cooperation ratio per seed per tournament type.",
       x = "coop ratio",
       y = "round") +
  xlim(1000,9000)
```

```{r}
outliers %>%
  mutate(seed = as.factor(Seed)) %>%
  ggplot() +
  geom_point(aes(S.D., Counts, color = seed)) +
  geom_smooth(aes(S.D., Counts), color = "black") +
  facet_wrap(~tournament) +
  labs(title = "The instability of the average rage of cooperation.",
       x = "s.d.",
       y = "deviation from average") 
```

</body>
